---
title: 
author: 
output: pdf_document
#bibliography: "AMPYaganes.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Methodology

### Food web construction

The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and references that confirm each of them. Table 2 is the species list with details on trophic species cases (aggregated taxa).

## Results

```{r ref_plot, echo=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

# Load packages
library(tidyverse)
library(ggplot2)
library(multiweb)
library(dplyr)
library(igraph)
library(knitr)
library(kableExtra)
library(pander)

# Load data
load("../Datos/analisisdatos.rda")


#Table 1. Complexity properties
smallworld<-sample(c("TRUE"))
propcomplejidad<-cbind(propcomplejidad, smallworld)
borrar<-c("Top","Basal","TLmax","LOmnivory","Components","Vulnerability","VulSD","Generality","GenSD", "Cannib")
Tabla1<- propcomplejidad[ , !(names(propcomplejidad) %in% borrar)]
Tabla1ok<-Tabla1 %>% rename (Species = Size, Interactions=Links, Omn=Omnivory, Clus.coef=Clustering, SW=smallworld)

knitr::kable(Tabla1ok %>% arrange(., (Species)), booktabs = TRUE, col.names = c("Species","Omn","Interactions", "LD","Connectance","Pathlength","Clus.coef","TLmean","SW"), caption = "Complexity properties.") %>% 
  column_spec(1:9, width="2cm") %>% 
  column_spec(9, width="10cm") %>% 
  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
  landscape()



#Figura 1. Histogram
par(mfrow = c(1,1))
grado<-as.data.frame(degree(gok))
pl<-ggplot(grado,aes(x=degree(gok)))
pl + geom_histogram(binwidth = 1,col='black', fill='black', alpha=0.6) + xlab('Grado') + ylab('Frecuencia') + ggtitle('Distribucion de grado')

#binwidth = ancho de la barra
#alpha = transparencia del grafico


# Figure 2. Centrality graphs
par(mfrow = c(1,3))
set.seed(1)  # mantiene la posición de las especies
plot_troph_level(gok, vertex.size=sqrt(V(gok)$degree.total), ylab = "Trophic level", main = "Degree")
set.seed(1)
plot_troph_level(gok, vertex.size=sqrt(V(gok)$betweeness), main = "Betweenness")
set.seed(1)
plot_troph_level(gok, vertex.size=10^3*V(gok)$closeness,main = "Closeness")


```
## Supplementary material


```
# Table 1. List of species
borrar_sp<-c("Filum", "Clase", "Orden", "Familia","Género","Nombre.común","Hábitat","Dominio.CB","Dominio.CCA","Dominio.CCH","Expertise")
listadeespecies<-especies1[ , !(names(especies1) %in% borrar_sp)]
Listofspecies<-listadeespecies %>% rename (Species = Especie.trófica, Reference=Referencia, Link=Enlace)

knitr::kable(Listofspecies%>% arrange(., (Species)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("ID","Species","Reference", "Link"), caption = "List of trophic species") %>% 
  column_spec(1:3, width="2cm") %>% 
  column_spec(4, width="14cm") %>% 
  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
  landscape()
```

