---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
# classoption: landscape
bibliography: AMPYaganes.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

# Supplementary Material for 'Enhancing the analysis of the pelagic food web within the oceanic Marine Protected Area Yaganes and its surrounding areas'

## Methodology

### Food web construction

The following figure and tables summarise the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Yaganes ecosystem.
Table 1 is the complete list of trophic interactions and references that confirm each of them. Table 2 is the species list with details on trophic species cases (aggregated taxa).

\newpage
\blandscape

```{r tableS1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load packages
require(tidyverse)
require(knitr)
require(dplyr)
require(kableExtra)
require(pander)

# Load data
load("../Datos/datosdepurados_apr24.rda")

# Filter interaction list
int_tbl <- lista_interaccionesok %>% 
  dplyr::select(Prey, Predator, Reference, Link, Observations) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Table S1
pandoc.table(int_tbl %>% arrange(., (Predator)) %>% mutate(Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator), Reference = paste('\\tiny', Reference), Link = paste('\\tiny', Link), Observations = paste('\\tiny', Observations)), style="multiline", split.tables = Inf, justify = c("left","left","left","left","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Yaganes ecosystem (MPAY).")

```

\newpage

```{r tableS2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load data
load("../Datos/analisis_datos_apr24.rda")

# Filter species list
sp_tbl <- sp_level %>% 
  dplyr::select(name, degree.total, closeness, betweeness, TL, IEC) %>% 
  # add taxonomic level
  mutate(TaxLevel = case_when(str_detect(name, "dae") ~ "Family",
                              name %in% c("Detritus","Necromass","Ichthyoplankton","Zooplankton","Phytoplankton") ~ "NA",
                              name %in% c("Copepoda_others","Gastropoda_others","Ostracoda","Polyplacophora","Polychaeta") ~ "Class",
                              name %in% c("Amphipoda","Decapoda_others","Calanoida","Isopoda_others","Squaliformes","Cumacea") ~ "Order",
                              name == "Foraminifera" ~ "Phylum",
                              str_detect(name, "_sp|_spp") ~ "Genus",
                              str_detect(name, "Lepidonotothen") ~ "Genus",
                              TRUE ~ "Species"))

# Table S2
pandoc.table(sp_tbl %>% arrange(., (IEC)) %>% 
               mutate(across(where(is.numeric), round, 3)) %>% 
               rename("Species"="name", "Degree"="degree.total", "Closeness"="closeness", "Betweeness"="betweeness", "KSI"="IEC"), style="multiline", split.tables = Inf, justify = c("left","center","center","center","center","center","right"),
             caption = "List of species for the food web of the Marine Protected Area Yaganes. TL: Trophic Level; KSI: Keystone Species Index. TaxLevel: Taxonomic Level. Ordered by the KSI.")

```


\elandscape
